Supplementary appendix

### 2018-06-19 paper2_APPENDIX.Rmd
Add files via upload

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_comb_robust_3 = SVIVA2_01_comb %>%
  filter(#RECOGNIZE_SVIVA_logo>1,
         RECOGNIZE_campaign>1)

@@

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_comb_robust_4 = SVIVA2_01_comb %>%
  filter(RECOGNIZE_SVIVA_logo>1)

@@

[Introduction]

Greetings,

We are researchers from the Department of Political Science at the Hebrew University.
The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly.

The questionnaire filling time is about 5-10 minutes.

It is important for us to clarify that the questionnaire is being voluntarily filled out. Filling out the questionnaire and submitting it are an agreement to participate in the research.

In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only.
Non-consent to participate will be expressed in non-filling of the questionnaire.

The questionnaire is phrased in masculine form but addresses both men and women.

Thank you for your cooperation!

@@

[Pre-manipulation items]

First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.

@@

[Manipulation of perceived personal relevance of policy plans: participants are randomly assigned to treatment and control conditions].

@@

Now, we would like to ask you a few general questions about your interest in environmental issues.

@@

@@

**What is the name of the locality where you live today?**

**In your opinion, what is the most disturbing environmental problem in your area?**

@@

Now, we would like to ask you a few general questions about your area of occupation

@@

**What is your field of profession/study?**

@@

**What, in your opinion, might attract people to choose your occupation??**

@@

Next, we will present you two policy plans on specific environmental issues. The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.

At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.

[Participants are presented with the two policy plans. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]

Now, we'd like to ask you a few questions about your position on the policy for ["Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay"]:

@@

[Questions about elaboration and personal relevance]

The following sentences describe the way in which you read the latest policy plan that regarded to ["Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay"].

@@

Try recalling the content of the latest policy plan.
[Each subjects was asked about the latest policy plan presenter to her]

@@

8. Other: ___

@@

[Demographic questions]

We would like to ask you a few general questions:

**How old are you?**

@@

**What is your place of residence?**

@@

**State the name of the place where you lived at high-school graduation**

@@

[Manipulation check for symbols]

[For real symbols]:
Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.

This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"

@@

This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"

@@

[For fake symbols]:
Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.

This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"

@@

We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.

[Respondents are displayed with the two "real" images, and then asked the following two questions]

@@

[For no symbols]:

Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.

[Respondents are displayed with the two "real" images, and then asked the following two questions]

@@

[Debrief]

Thank you very much for participating in the study.

Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently. The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy. [For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]

>>>>

SVIVA2_comb_robust_3 = SVIVA2_01_comb %>%
  filter(#RECOGNIZE_SVIVA_logo>1,
         RECOGNIZE_campaign>1)

SVIVA2_comb_robust_4 = SVIVA2_01_comb %>%
  filter(RECOGNIZE_SVIVA_logo>1)
```

In the tables below, I present additional robust analyses for the effect of symbols on trust in policy and its interaction with the information of the policy plans. In **Table A3**, I replicate table 1 of the main paper on the full, unfiltered sample, excluding subjects who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`). In **Table A4**, I add a set of control variables. In **Table A5** and **Table A6**, I exclude those subjects who did not recognize the real symbols which were included in the communications. Table A5 excludes those who did not recognize the campaign images (n_subjects = `r SVIVA2_comb_robust_3 %>%distinct(IP) %>% nrow()`) and Table A6 excludes those who did not recognize EPM's logo (n_subjects = `r SVIVA2_comb_robust_4 %>%distinct(IP) %>% nrow()`). Finally, in **Table A7**, I add interactions with the policy plan, to examine whether the effect of the symbols were significanly different for these two policies. All these analyses are random-effect GLS regressions clustered at the subject level, similarly to the main models presented in the paper.

In all these supplementary analyses, the main effect of the real symbols on trust in policy is significant, and the interaction bewteen the real symbols and the weak inforamtion remains positive and significant.

@@

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy (combined)"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized coefficients. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

@@

Below is the full text of the survey. Additional comments are presented in square beackets. The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here. The original Qualtrics file is available upon request.

**Greetings, We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. The questionnaire filling time is about 5-10 minutes.**

**It is important for us to clarify that the questionnaire is voluntary. Filling out the questionnaire and submitting it represent your agreement to participate in the research. In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only. Non-consent to participate will be expressed in not filling of the questionnaire. The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**

**Thank you for your cooperation!**

@@

**First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.**

@@

[The following section includes a manipulation of perceived personal relevance of policy plans. Participants were randomly assigned to treatment and control conditions, as detailed below].

@@

**Now, we would like to ask you a few general questions about your interest in environmental issues.**

@@

**In which residential area do you currently live?**

@@

**What is the name of the locality where you live today? _________________**

**In your opinion, what is the most disturbing environmental problem in your area? ________________________________________**

@@

**Now, we would like to ask you a few general questions about your area of occupation**

@@

**What is your field of profession/study? ______________**

@@

**What, in your opinion, might attract people to choose your occupation?? _________________________________________**

@@

**Next, we will present you two policy plans on specific environmental issues. The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.**

**At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.**

[Participants are then presented with the two policy plans (air-pollution and recycling), in a random order. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]

**Now, we'd like to ask you a few questions about your position on the policy for "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay":**

@@

**The following sentences describe the way in which you read the latest policy plan that regarded to "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay".**

@@

**Try recalling the content of the latest policy plan.**
[Each subjects was asked about the latest policy plan presenter to her]

@@

8. Other: ______

@@

**We would like to ask you a few general questions:**

**HWhat is your age?**
10----20----30----40----50----60----70----80

@@

**What is your place of residence? ___________**

@@

**State the name of the place where you lived at high-school graduation: ____________**

@@

[The following section is a manipulation check for the symbols]

[For subjects assigned to the real symbols]:
**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**

**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**

@@

**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**

@@

[For subjects assigned to the fake symbols]:
**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**

**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**

@@

**We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.**

[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]

@@

[For subjets assigned to the no symbols]:

**Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.**

[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]

@@

**Thank you very much for participating in the study. Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently. The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy. [For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]**
